Notes on two photon scattering of the molecular state

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] typo in summary title. Raggedright. Figure hight
[notes/two-photon-broadening] coupling down

\begin{document}

\maketitle

@@

\subsubsection{Single photon off resonance scattering from coupled excited state}
\begin{wrapfigure}{R}{7.3cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 3.5);

@@

More directly related to the excited state linewidth measurement, we can first couple the
two excited states together with $\Omega_2$.\\

@@

\subsubsection{Summary for two photon coupling down}

@@

\subsection{Two photon coupling down}

>>>>

\begin{document}
\maketitle

\raggedright

@@

\subsubsection{Single photon off resonance scattering from coupled excited state}
\begin{wrapfigure}[10]{R}{7cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 3.5);

@@

More directly related to the excited state line width measurement, we can first couple the
two excited states together with $\Omega_2$.\\

@@

\subsubsection{Summary for two photon coupling up}

@@

\subsection{Two photon coupling down}
\begin{wrapfigure}{R}{8.4cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 4);
      \draw[line width=1] (1, 0) node[left] {$|0\rangle$} -- (2, 0);
      \draw (1, 0.1) -- (2, 0.1);
      \draw (1, 0.2) -- (2, 0.2);
      \node[rotate=90] at (1.5, 0.5) {$\cdots$};
      \node[left] at (1, 0.5) {$|n\rangle$};
      \draw (1, 0.8) -- (2, 0.8);
      \draw (1, 0.9) -- (2, 0.9);
      \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);

      \draw[line width=1] (1, 3.5) node[left] {$|e\rangle$} -- (2, 3.5);

      \draw[dashed] (1, 3) -- (2, 3);
      \draw[->, line width=1,green!80!black] (1.5, 3) -- node[right] {$\Omega_2$} (1.7, 1.2);
      \draw[->, line width=1,blue] (1.2, 0) -- node[above left] {$\Omega_1$} (1.5, 3);

      \node[above] at (1.5, 3.65) {(A)};
      \begin{scope}[shift={(1.4, 0)}]
        \draw[line width=1] (1, 0) -- (2, 0);
        \draw (1, 0.1) -- (2, 0.1);
        \draw (1, 0.2) -- (2, 0.2);
        \node[rotate=90] at (1.5, 0.5) {$\cdots$};
        \draw (1, 0.8) -- (2, 0.8);
        \draw (1, 0.9) -- (2, 0.9);
        \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);

        \draw[line width=1] (1, 3.5) -- (2, 3.5);

        \draw[dashed] (1, 3) -- (2, 3);
        \draw[<->, line width=1,blue] (1.65, 0) -- node[above left] {$\Omega_1$} (1.65, 3);

        \node[above] at (1.5, 3.65) {(B)};
      \end{scope}
      \begin{scope}[shift={(2.8, 0)}]
        \draw[line width=1] (1, -0.5) node[left] {$|\!-\!1\rangle$} -- (2, -0.5);
        \draw[line width=1] (1, 0) -- (2, 0);
        \draw (1, 0.1) -- (2, 0.1);
        \draw (1, 0.2) -- (2, 0.2);
        \node[rotate=90] at (1.5, 0.5) {$\cdots$};
        \draw (1, 0.8) -- (2, 0.8);
        \draw (1, 0.9) -- (2, 0.9);
        \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);

        \draw[line width=1] (1, 3.5) -- (2, 3.5);

        \draw[dashed] (1, 3) -- (2, 3);
        \draw[<->, line width=1,green!80!black] (1.51, 3) -- (1.7, -0.5);
        \node[above right,green!80!black] at (1.6, 1.5) {$\Omega_2$};
        \draw[<->, line width=1,blue] (1.2, 0) -- node[above left] {$\Omega_1$} (1.49, 3);

        \node[above] at (1.5, 3.65) {(C)};
      \end{scope}
      \begin{scope}[shift={(4.2, 0)}]
        \draw[line width=1] (1, 0) -- (2, 0);
        \draw (1, 0.1) -- (2, 0.1);
        \draw (1, 0.2) -- (2, 0.2);
        \node[rotate=90] at (1.5, 0.5) {$\cdots$};
        \draw (1, 0.8) -- (2, 0.8);
        \draw (1, 0.9) -- (2, 0.9);
        \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);

        \draw[line width=1] (1, 3.5) -- (2, 3.5);

        \draw[dashed] (1, 3) -- (2, 3);
        \draw[->, dashed, line width=0.3,blue] (1.5, 3) -- node[right] {$\Omega_1'$} (1.7, 1.2);
        \draw[->, line width=1,blue] (1.2, 0) -- node[above left] {$\Omega_1$} (1.5, 3);

        \node[above] at (1.5, 3.65) {(D)};
      \end{scope}
      \begin{scope}[shift={(5.6, 0)}]
        \fill[red,opacity=0.2] (1.8, -0.5) rectangle (2.5, 0.5);
        \draw[line width=1] (1, 0) -- (1.7, 0);
        \draw (1, 0.1) -- (1.7, 0.1);
        \draw (1, 0.2) -- (1.7, 0.2);
        \node[rotate=90] at (1.35, 0.5) {$\cdots$};
        \draw (1, 0.8) -- (1.7, 0.8);
        \draw (1, 0.9) -- (1.7, 0.9);
        \fill[opacity=0.2] (1, 1) rectangle (1.7, 1.5);

        \draw[line width=1] (1, 3.5) -- (2.5, 3.5);

        \draw[dashed] (1, 3) -- (2.5, 3);
        \draw[<->, line width=1,blue] (1.4, 0) -- node[above left] {$\Omega_1$} (1.75, 3);
        \draw[<->, line width=1,blue] (2.1, 0) -- node[above right] {$\Omega_1'$} (1.75, 3);

        \node[above] at (1.75, 3.65) {(E)};
      \end{scope}
    \end{tikzpicture}
  \end{center}
  \caption{Coupling to ground state motional continuum. (A) Raman into motional continuum.
    (B) Single ground HF state, single laser frequency. (C) Single ground HF state,
    two frequencies for molecular Raman. (D) Unexpected sideband in laser.
    (E) Zero energy continuum.}
  \label{two-down}
\end{wrapfigure}

The potential second photon coupling down pathway is very similar.
See \mbox{figure \ref{two-down}A}. The loss is caused by the ground state (atomic or molecular)
coupling to the ground motional continuum.\\

We can also directly apply the two points from the summary above.
\begin{enumerate}
\item In order to calculate ground state loss, we should consider the Raman process,
  which will likely have very different motional energies compared to the motional energy
  coupling down from the excited state.
\item The excited state is coupled to an atomic motional continuum and the resulting loss
  will have a very different profile from then $\Delta^{-2}$ scaling. Even if we
  see a broadening of the excited state due to this coupling, it does not mean much
  for the corresponding ground state loss rate.
\end{enumerate}

The two kinds of ground state scattering measurements we have are atomic state PA rate
and molecular state scattering (using Raman transition).
Assuming the laser is clean and no other states are involved,
\begin{enumerate}
\item For atomic scattering rate (\mbox{figure \ref{two-down}B}), there is only
  one frequency so the Raman process can only come back down to the same energy as
  the initial state, which is not in an continuum.
\item For molecular scattering rate during transfer (\mbox{figure \ref{two-down}C}),
  similarly, the only energy the molecular state could couple to is the initial energy
  or a deeper bound state (2x the binding energy). Neither of these is a continuum either.\\
  The atomic state can indeed be coupled to the continuum but it should be much weaker than
  the molecular state (the up leg is much smaller) and we have not measured a decrease in
  atomic 2-body lifetime when the Raman beam is turned on.
\end{enumerate}
Therefore, in order to generate any loss from this process for the ground state,
we need to have either,
\begin{enumerate}
\item Additional frequencies in the laser (\mbox{figure \ref{two-down}D}) which
  can couple the state of interest to the motional continuum. Or,
\item Continuum that has zero energy (\mbox{figure \ref{two-down}E}) that the Raman beam
  can couple to.\\
  Candidate for this continuum includes the center of mass (COM) motional states and
  the motional continuum from other HF states.\\
  The COM motional continuum actually also starts at a positive energy so it doesn't seems
  possible. The continuum from other HF states is much more promising especially since
  we know that the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state has a strong coupling to the molecular excited states.
  However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
  the HF state with the lowest energy.
\end{enumerate}

\subsection{Summary for interpreting and connecting excited state and ground state results}

From the discussion above, we see that no matter what kind of couple we have,
the excited state line width may not be directly related to the life time in the tweezer
of the corresponding frequency. For up coupling, the result is more closely related
to the lifetime for tweezer of the average frequency, whereas for down coupling,
the lifetime may not be related to the excited state line width at all.
